The universal property of direct integrals in W$^*$-categories

### 2018-05-01 direct_integrals.tex
historical comment

>>>>

As far as we know, the first definition of infinite direct sums has been given in~\cite[p.~100]{wstarcat} in the form~\ref{biprodsum}. From our perspective, it is preferable to replace this definition by a universal property as in Definition~\ref{directsumdef}, and regard the original definition as an alternative characterization instead.
